Temporal stability in human interaction networks

### 2015-07-01 paper.tex
untitled typo :P

\subsection{Availability data and scripts}\label{scripts}
In order to share routines with the scientific community and the whole of the society,
all the required software to achieve the results reported in this article,
including tables and figures in the Supporting Information,
are available through a public domain Python package and an open Git repository~\cite{gmanePack}.

>>>>

\subsection{Availability of data and scripts}\label{scripts}
In order to share routines with the scientific community and the whole of the society,
all the required software to achieve the results reported in this article,
including tables and figures in the Supporting Information,
are available through a public domain Python package and an open Git repository~\cite{gmanePack}.
